Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections at the LArIAT experiment

### 2018-08-13 Chapter-3/3-TheLArIATExperiment.tex
s

%%%%%%%%%%%%%%%%%%%%%
As in any other LArTPC, argon purity is a crucial parameter for LArIAT. Indeed, the presence of contaminants affects both the basic working principles of a LArTPC, as shown in Section \ref{sec:LArTPCWorkingPrinciple}: electronegative contaminants such as oxygen and water decrease the number of ionization electrons collected on the wires after drifting through the volume. In addition, contaminants such as Nitrogen decrease the light yield from scintillation light, especially in its slow component.
In LArIAT, contaminations should not exceed the level of 0.2 parts per billion (ppb). We achieve this level of purity in several stages. The specifics required for the commercial argon bought for LArIAT are 2 parts per million (ppm) oxygen, 3.5~ppm water, and 10~ppm nitrogen. This argon is monitored with the use of commercial gas analyzer.
Argon is stored in a dewar external to LArIAT hall and filtered before filling the TPC. %The argon is delivered from the commercial dewar to the cryostat through 2.54~cm diameter schedule 10 stainless steel piping.  The piping was insulated with 20.32~cm of polyurethane foam by the manufacturer.  The piping was cleaned to remove oil and grease before being welded into the system. 
LArIAT uses a filtration system designed for the Liquid Argon Purity Demonstrator (LAPD)~\cite{LAPD}: half of a 77~liter filter contains a 4A molecular sieve (Sigma-Aldrich~\cite{sigma-aldrich}) able to remove mainly water, while the other half contains BASF~CU-0226~S, a highly dispersed copper oxide impregnated on a high surface area alumina, apt to remove mainly oxygen~\cite{basf}. A single pass of argon in the filter is sufficient to achieve the necessary purity, unless the filter is saturated. In case the filter saturates, the media needs to be regenerated by using heated gas; this happened twice during the Run II period\footnote{We deemed the filter regeneration necessary every time the electron lifetime dropped under 100 \textmu s.}. The electron lifetime during the full LArIAT data taking are shown in Figure \ref{fig:Elifetime}.
The filtered argon reaches the inner vessel via a liquid feedthrough which is routed to the bottom of the cryostat. Argon is not recirculated in the system; rather, it boils off and vents to the atmosphere. During data taking, we replenish the argon in the cryostat every 6 hours to keep the TPC high voltage feedthrough and cold electronics always submerged. In fact, we constantly monitor the level, temperature, and pressure of the argon both in the commercial dewar and inside the cryostat during data taking. 
\subsection{LArTPC: Charge Collection}\label{sec:TPCCharge}
The LArIAT Liquid Argon Time Projection Chamber is a rectangular box of dimensions 47 cm (drift) x 40 cm (height) x 90 cm (length), containing 170 liters of Liquid Argon.
The LArTPC three major subcomponents are 
\begin{itemize} 
\item[1)] the cathode and field cage,
\item [2)] the wire planes, 
\item [3)] the read-out electronics. %
\end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%
As in any other LArTPC, argon purity is a crucial parameter for LArIAT. Indeed, the presence of contaminants affects both the basic working principles of a LArTPC, as shown in Section \ref{sec:LArTPCWorkingPrinciple}: electronegative contaminants such as oxygen and water decrease the number of ionization electrons collected on the wires after drifting through the volume. In addition, contaminants such as Nitrogen decrease the light yield from scintillation light, especially in its slow component.
In LArIAT, contaminations should not exceed the level of 0.2 parts per billion (ppb). We achieve this level of purity in several stages. The specifics required for the commercial argon bought for LArIAT are 2 parts per million (ppm) oxygen, 3.5~ppm water, and 10~ppm nitrogen. This argon is monitored with the use of commercial gas analyzer.
Argon is stored in a dewar external to LArIAT hall and filtered before filling the TPC. %The argon is delivered from the commercial dewar to the cryostat through 2.54~cm diameter schedule 10 stainless steel piping.  The piping was insulated with 20.32~cm of polyurethane foam by the manufacturer.  The piping was cleaned to remove oil and grease before being welded into the system. 
LArIAT uses a filtration system designed for the Liquid Argon Purity Demonstrator (LAPD)~\cite{LAPD}: half of a 77~liter filter contains a 4A molecular sieve able to remove mainly water, while the other half contains BASF~CU-0226~S, a highly dispersed copper oxide impregnated on a high surface area alumina, apt to remove mainly oxygen. A single pass of argon in the filter is sufficient to achieve the necessary purity, unless the filter is saturated. In case the filter saturates, the media needs to be regenerated by using heated gas; this happened twice during the Run II period\footnote{We deemed the filter regeneration necessary every time the electron lifetime dropped under 100 \textmu s.}. The electron lifetime during the full LArIAT data taking are shown in Figure \ref{fig:Elifetime}.
The filtered argon reaches the inner vessel via a liquid feedthrough which is routed to the bottom of the cryostat. Argon is not recirculated in the system; rather, it boils off and vents to the atmosphere. During data taking, we replenish the argon in the cryostat every 6 hours to keep the TPC high voltage feedthrough and cold electronics always submerged. In fact, we constantly monitor the level, temperature, and pressure of the argon both in the commercial dewar and inside the cryostat during data taking. 
\subsection{LArTPC: Charge Collection}\label{sec:TPCCharge}
The LArIAT Liquid Argon Time Projection Chamber is a rectangular box of dimensions 47 cm (drift) x 40 cm (height) x 90 cm (length), containing 170 liters of Liquid Argon.
The LArTPC three major subcomponents are 
\begin{itemize} 
\item[1)] the cathode and field cage,
\item [2)] the wire planes, 
\item [3)] the read-out electronics. %
\end{itemize}
